---
title: "Gov 50 Final Project"
author: "Isabela Gonzalez-Lawand"
description: "Understanding which ages are most impacted by crime in LA area"
output:
  distill::distill_article:
    self_contained: false
---
install.packages("distill")


## Project thoughts
Milestone 1 
 - I am interested in exploring data related to the way different genders votes in national elections compared to local elections. 

Update: Project will now be about Crime in LA and the relationship between age and sex of victims. 

## Project thoughts 
Project MILESTONE 2 

The data set I am taking a look at is Crime Data in Los Angles from 2020 to present day. In looking over this data I have come up with the question of, does the specific area in Los Angles impact the amount of crime/crime rate that is reported. So for example is the crime rate in Central higher than it is in West Valley or Hollywood. I hypothesis that the areas of Los Angles that are more populated such as Central LA that cover areas such as LAX will report higher rates of crime also considering that Central LA covers the large portion of cities in LA compared to smaller towns/areas such as West Valley. I hypothesize this because generally larger cities have higher crime rates overall in the Unites States compared to smaller/less populated areas across the country. My sample takes a look at every crime reported from the year 2020 to 2023 in the Los Angles are, including the type of crime committed, and where the crime was committed. My explanatory variable is V6 which showcases where the crime was committed and in looking at this I can also filter the data to organize how many crimes were committed in that area. Another area of interest that could be analyzes is variable V10 that describes the type of crimes that were committed and analyzing the relationship between the types of crimes committed and the area in which the crimes were committed and analyze if there's a relationship there. The outcome variable is the crime and the number of crime that is committed in a particular area. In the data I was able to form my hypothesis because there was a large number of data recorded for Central LA that has more violent crimes reported than the number of crimes reported in areas such as West Valley LA. 

Project update: Most victims despite being male or female seem to be between the ages of 30-45 and the outliars of crime seem to land amoungs younger ages especially in children and infants as well as the elderly so people in the ages of 60 and older. 

Project Update: Making a bar plot seemed more approriate and while there was a lot more data than maybe was needed we were able to showcase the entirety of the data 

## Project Thoughts Milestone 3 
```{r}
library(tidyverse)
Crime_Data_from_2020_to_Present |>
    count(V12, V13) |>
  ggplot(aes(x = V13, y = n , fill = V12)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Crime in Los Angeles",
       x = "Sex of Victim",
       y = "Number of Victims")
```


##Project Milesetone 4
```{r}
library(tidyverse)
Crime_Data_from_2020_to_Present |>
  count(V12, V13) |>
  ggplot(aes(x = V13, y = n, color = factor(V12))) +
  geom_point() +
  labs(title = "Crime in Los Angeles",
       x = "Age of Victim",
       y = "Number of Victims",
       color = "Victims Age by Color") 



```
##Final Project Report 
Introduction: 
describe the research question and main hypothesis; describe why it is important. (1-2 paragraphs) (2pts)

 Introuduction: 
    For my final project I decided to research Crime in the Los Angeles area, my specific question being around the vicitms of crime. In my research I was looking for the answer to. my question of what age groups in the Los Angeles area are most impacted by crime and if the age changes based on gender. My hypothesis was that those who were in their 60-80's who were women would be the ones who were most at stake for being victims of crime in the area. This is an imporatnt topic because Los Angeles is one of the most populat cities in the United States and that popularity isn't always sunshine and rainbows, understanding who the targets of crime are will help us get an understanding of what areas need more policing, what groups need more advocates, and allow us to come up with a plan in order to stop the crime from occuring in the future. The reason my hypohtesis says that people ages 60 and up would be easier to target is because this is a vulernable group that unlike children does not have anyone to watch over there and physcially have a harder time doing things making it easier for them to fall victims of this. Gender is important to understand and the role it plays because we live in a society where women are constantly under attack so when you put an older woman in LA I predicted that this particular group would be at higher risk than any other group. 

Data: 
##Graph 1
```{r}
library(tidyverse)
Crime_Data_from_2020_to_Present |>
    count(V12, V13) |>
  ggplot(aes(x = V13, y = n , fill = V12)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Crime in Los Angeles",
       x = "Sex of Victim",
       y = "Number of Victims")
```
    In collecting my data I used data from the LAPD that took a look at crimes in 2020 all over LA. These crimes ragned from robbery all the way to murder. This data also included information such as specific locations in LA where crimes were being committed, gender, and so much more. But for my data I focused on the ages of the victims from younger than 1 to as old as 90 years old and focused on the gender of the victims (some of which identified as X whihc is niether male nor female and in some cases meant that the victim was unidentifiable). In my first graph I made a bar plot in this plot we see there range of data and we see a bell curve being formed with each of the colors representing a different age and we also see that there are two bell curves that are being made one of them over the letter F (female victims) and one of them over the letter M (male victims). Taking a closer look at the data I began to realize that there was a matter amoung both and that was that we see the increase in numbers for victims when they are around the age of 30-55. This came as a shock to me because I was expecting there to be a larger curve for ages 60-80. When thinking more about who lives in the LA area I started to think that maybe the reason that the curve is at a younger point is because this area is mostly made of up of people 20-50ish. 
    Taking a look at the difference between men and women in this graph you can see a slight spike for men in there early to late 20's seeming to be more impacted by crime than women. It seems to be that the first time that we really see the graph move up is for kids in their early teens and then we see a large part of the graph being green and orange covering an age from from 20 to about 50 and then we see a a slow drop after with very little crime being associated with people around the age of 80. While crime spiked for men in their 20s we see a very similiar spike for women but in thier early teens. Now from this data a lone we cannot know why teen girls are slightly more attacked than male boys or why men in their 20's are slightly more attacked than womne. These spikes do seem to be the outliars however meaning that gender may not play as large or a role as our hypothesis originally thought. 
      
Results: 
##Graph 2
```{r}
library(tidyverse)
Crime_Data_from_2020_to_Present |>
  count(V12, V13) |>
  ggplot(aes(x = V13, y = n, color = factor(V12))) +
  geom_point() +
  labs(title = "Crime in Los Angeles",
       x = "Age of Victim",
       y = "Number of Victims",
       color = "Victims Age by Color") 

```
  I wanted to ensure that the way I was thinking about this was correct so I wanted to put my data in and make a scatter plot where I could take a look at where most of the dots would land for both genders. And we see in the second graph how there is this cluster of all ages and out outliars are actually those in orange some of which were over the age of 100 and others which were under the age of 1. This is telling us that children under the age of 1 are not common victims of crime in LA they are a population that is looked after more, who have parents that are taking care of them around the clock, so this population being an outliar is not suprising. Taking a look at our second group of outliars which showed to be people older than 90 it is show casing that this overall is still a vulernable group but specifically when it comes to being victims of crime in LA this is not a target group for criminals. On the other hand this graph also showed that younger groups such as those in their late 20's to 30's and those in their early to late 50's were victims are higher rates with more of them being victims of crtime than any other group. 
      One of the most important things to understand about both of thrse graphs is that gender was not something that played a larger role or demonstrated a visiual difference in numbers. On average it seems that men and women both had more crimes depending on their age rather than their gencder. For exmaple in both graphs we see about the same amount of green and blue with no gender having more than the other. This is important because it showcases that there was a part of our data that wasn't making the impact that we orginally thought it would. Now, this is not to say that women or men do not have a difference in thr amount of violence committed towards each group but in this sepcifc study it shows that criminals during 2020 cardd more about the age of the person rather than the gender. 
      
    
Conclusion: 
    In conclusion, my hypohtesis ended up being incorrect. I predicted that women in their 60s-80 would be victims of crime are higher rate than men. However through my research I learned that gender did not play as a big of a role in the number of victims of crime as age did. Comparing the results for both men and women there were small spike in outliars such as young teen girls being higher rates of victims than young teen boys and men in their 20's being victims at higher rates than women in their 20's. My research while conducted thouroughly was not perfect and had it's limiations.My data soley looked at the year 2020 and did not consider that in this year many people were left homeless and without jobs, not to mention 2020 is the exception when it comes to time not the rule. So maybe I should have taken a look at data from other year of compared 2020 data to 2023 data to see if there was a difference and maybe even investigated why. 
      